func-descr.template

### 2025-11-13 reports/capstone-movielens.site/work/func-descr.template.Rmd

#### [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.helper-func.tmpl}
\

::: { #func.helper-func.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
helper-func.tmpl()

@@

::: { #func.helper-func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.helper-func.tmpl.args. .sidebar }
  - **:** ;

:::
::: { #func.helper-func.tmpl.args. .sidebar }
  - **:** ;

@@

::: { #func.helper-func.tmpl.details .sidebar }
##### Details
\

@@

::: { #func.helper-func.tmpl.value .sidebar }
##### Value
\

@@

::: { #func.helper-func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
:::
:::

@@

### Overal Mean Rating (OMR) Model Functions
\

@@

::: {.noteblock data-latex=""}
The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) script on _GitHub_.
:::
:::

@@

@@

::: {.noteblock data-latex=""}
The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
:::
:::

>>>>

#### [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_helper_func.tmpl}
\

::: { #func.cmmn_helper_func.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
cmmn_helper_func.tmpl()

@@

::: { #func.cmmn_helper_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.cmmn_helper_func.tmpl.args. .sidebar }
  - **:** ;

:::
::: { #func.cmmn_helper_func.tmpl.args. .sidebar }
  - **:** ;

@@

::: { #func.cmmn_helper_func.tmpl.details .sidebar }
##### Details
\

@@

::: { #func.cmmn_helper_func.tmpl.value .sidebar }
##### Value
\

@@

::: { #func.cmmn_helper_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
:::
:::

@@

## Model Helper Functions
### Overal Mean Rating (OMR) Model Functions
\

@@

::: {.noteblock data-latex=""}
The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) script on _GitHub_.
:::
:::

@@

### UME Model Utility Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
:::

#### [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) Function {#func.ume_helper.tmpl}
\

::: { #func.ume_helper.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
ume_helper.tmpl()

::: { #func.ume_helper.tmpl.args .sidebar }
##### Arguments
\

::: { #func.ume_helper.tmpl.args. .sidebar }
  - **:** ;

:::
::: { #func.ume_helper.tmpl.args. .sidebar }
  - **:** ;

::: { #func.ume_helper.tmpl.details .sidebar }
##### Details
\

::: { #func.ume_helper.tmpl.value .sidebar }
##### Value
\

::: { #func.ume_helper.tmpl.code .sidebar }
##### Source Code
\

The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
:::
:::

### UME Model Regularization
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [UME Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) script on _GitHub_.
:::

#### [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) Function {#func.ume_rglr_helper.tmpl}
\

::: { #func.ume_rglr_helper.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
ume_rglr_helper.tmpl()

::: { #func.ume_rglr_helper.tmpl.args .sidebar }
##### Arguments
\

::: { #func.ume_rglr_helper.tmpl.args. .sidebar }
  - **:** ;

:::
::: { #func.ume_rglr_helper.tmpl.args. .sidebar }
  - **:** ;

::: { #func.ume_rglr_helper.tmpl.details .sidebar }
##### Details
\

::: { #func.ume_rglr_helper.tmpl.value .sidebar }
##### Value
\

::: { #func.ume_rglr_helper.tmpl.code .sidebar }
##### Source Code
\

The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
:::
:::

## General Func Tempates -------------------------------------------------------

@@

::: {.noteblock data-latex=""}
The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
:::
:::
